### 2020-07-22 text/content.tex
Minor changes
Point to v2.0

\section*{Data Availability Statement}
The mobility data used in this paper \cite{SafeGraph2020-gn} is confidential, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium. Researchers interested in access to the data can apply at https://www.safegraph.com/covid-19-data-consortium. After signing a Data Agreement, access is granted within a few days. The authors will assist with any reasonable replication attempts for two years following publication.

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Full table of sectors.}
\label{S1_File}
{\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry. ``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v1.3/data/derived/industry-index.csv}.

\paragraph*{S2 Full table of ZIP-codes.}
\label{S2_File}
{\bf Social distancing exposure by location.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the ZIP code. ``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v1.3/data/derived/location-index.csv}.

\paragraph*{S3 Data repository.}
\label{S3_URL}
{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v1.3}.

>>>>

\section*{Data Availability Statement}
The mobility data used in this paper \cite{SafeGraph2020-gn} is confidential, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium. Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium}. After signing a Data Agreement, access is granted within a few days. The authors will assist with any reasonable replication attempts for two years following publication.

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Full table of sectors.}
\label{S1_File}
{\bf Social distancing exposure by sector.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the industry. ``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/industry-index.csv}.

\paragraph*{S2 Full table of ZIP-codes.}
\label{S2_File}
{\bf Social distancing exposure by location.} The percentage share of workers in teamwork-intensive, customer-facing, and physical-proximity occupations within the ZIP code. ``Communication share'' refers to the share of workers who are either teamwork-intensive or customer-facing. ``Affected share'' refers to the share of workers in any of the three occupation groups. Available at \url{https://github.com/ceumicrodata/social-distancing/blob/v2.0/data/derived/location-index.csv}.

\paragraph*{S3 Data repository.}
\label{S3_URL}
{\bf Replication code and data.} Replication code and data are available at \url{https://github.com/ceumicrodata/social-distancing/tree/v2.0}.
